Data_visualization

### 2018-06-13 Rmd/Data_visualization.Rmd
adding pollen sizes of hydratated pollen (equatorial diameter)

library(ggplot2)
library(Hmisc)
library(Formula)
#load data

@@

#Pollen per anther, just one Convolvulaceae at the moment
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)
library(Hmisc)
library(Formula)

>>>>

library(ggplot2)
#load data

@@

#Pollen per anther, just one Convolvulaceae at the moment
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)
